\textsf{\textbf{Analyzing \textit{Streptococcus mutans} RNA-seq data\\using R packages}}

### 2012-01-13 package/smutans/inst/doc/smutans.Rnw
An BioC R package, GenomicRanges, is being tested.

@@

Table \ref{tab:goseq} 
shows functional categories enriched with target genes for predicted small
RNAs. Let's use \Rfunction{smutans.mannwhitney} to the package and other data
objects.
%-----------------------------------------------------------------------------
\begin{table}[!h]
\caption{{\bf Gene Ontology (GO) enrichments for differentially expressed
genes}}
\vspace{1ex}
\noindent \begin{centering}
\begin{tabular}{lcccl}
\hline 
small RNA & $q^a$ & count & GO & Description \\
\hline 
%-----------------------------------------------------------------------------
<<goseqUA159only,results=tex>>=
data( "smutans.genes.criteria" )
data( "smutans.go.genes" )
data( "smutans.cat.desc" )
smutans.mannwhitney( qval=0.05,
                   genes.criteria=smutans.genes.criteria,
                   go.genes=smutans.go.genes,
                   cat.desc=smutans.cat.desc )
@
%-----------------------------------------------------------------------------
\hline 
\end{tabular}
\par\end{centering}
\begin{flushleft}
$^a$False discovery rate estimated by the
Benjamini-Hochberg method.  All categories having at least ten genes and
$q\leq 0.05$ are displayed.\\ 
\end{flushleft}
\label{tab:goseq}
\end{table}
%-----------------------------------------------------------------------------

>>>>

We need ways of supporting the predicted transcripts. We need a way of using
expression levels and counts of starts and ends of short reads to predict
transcripts. For now, we just use an ad hoc method for finding transcript start
and end sites. A likelihood can be constructed by multiplying geometric
probabilities. Given a range of possible transcription boundaries we can find
estimates of positions and geometirc parmeter $p$ that maximize the likelihood
for both ends of a transcript.

\Rpackage{GenomicRanges} might be useful in 
<<tx,eval=FALSE>>=
source("http://www.bioconductor.org/biocLite.R")
biocLite("GenomicRanges")
@

@@

Table \ref{tab:goseq} 
shows functional categories enriched with target genes for predicted small
RNAs. Let's use \Rfunction{smutans.mannwhitney} to the package and other data
objects.
%-----------------------------------------------------------------------------
\begin{table}[!h]
\caption{{\bf Gene Ontology (GO) enrichments for differentially expressed
genes}}
\vspace{1ex}
\noindent \begin{centering}
\begin{tabular}{lcccl}
\hline 
small RNA & $q^a$ & count & GO & Description \\
\hline 
%-----------------------------------------------------------------------------
<<goseqUA159only,echo=FALSE,results=tex>>=
data( "smutans.genes.criteria" )
data( "smutans.go.genes" )
data( "smutans.cat.desc" )
smutans.mannwhitney( qval=0.05,
                   genes.criteria=smutans.genes.criteria,
                   go.genes=smutans.go.genes,
                   cat.desc=smutans.cat.desc )
@
%-----------------------------------------------------------------------------
\hline 
\end{tabular}
\par\end{centering}
\begin{flushleft}
$^a$False discovery rate estimated by the
Benjamini-Hochberg method.  All categories having at least ten genes and
$q\leq 0.05$ are displayed.\\ 
\end{flushleft}
\label{tab:goseq}
\end{table}
%-----------------------------------------------------------------------------
